ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-05-17 paper/paper.tex
just missing more tables

Since we were not able to identify any existing open-source software for Energy-Based Modelling that would be flexible enough to cater to our needs, we have developed a Julia package from scratch. In our development we have heavily drawn on the existing literature:~\citet{du2020implicit} describe best practices for using EBM for generative modelling;~\citet{grathwohl2020your} explain how EBM can be used to train classifiers jointly for the discriminative and generative tasks. We have used the same package for training and inference, but there are some important differences between the two cases that are worth highlighting here.

@@

In this section, we briefly discuss convergence conditions for CE and provide details concerning the actual implementation of our framework in Julia.

\subsubsection{A Note on Convergence}

@@

Our code base is integrated into a larger ecosystem of \texttt{Julia} packages that we are actively developing.

\subsection{Experimental Setup}\label{app:setup}
\subsection{Results}\label{app:results}

>>>>

Since we were not able to identify any existing open-source software for Energy-Based Modelling that would be flexible enough to cater to our needs, we have developed a \texttt{Julia} package from scratch. The package has been open-sourced, but to avoid compromising the double-blind review process, we refrain from providing more information at this stage. In our development we have heavily drawn on the existing literature:~\citet{du2020implicit} describe best practices for using EBM for generative modelling;~\citet{grathwohl2020your} explain how EBM can be used to train classifiers jointly for the discriminative and generative tasks. We have used the same package for training and inference, but there are some important differences between the two cases that are worth highlighting here.

@@

In this section, we briefly discuss convergence conditions for CE and provide details concerning the actual implementation of our framework in Julia.  
\subsubsection{A Note on Convergence}

@@

The core part of our code base is integrated into a larger ecosystem of \texttt{Julia} packages that we are actively developing and maintaining. To avoid compromising the double-blind review process, we only provide a link to an anonymized repository at this stage: \url{https://anonymous.4open.science/r/ECCCo-1252/README.md}.

\subsection{Experimental Setup}\label{app:setup}

\subsection{Results}\label{app:results}
